Typing a linear \picalc

### 2020-03-25 paper/paper.tex
Use commonly used symbols for capabilities

% Constructors
\newcommand{\PO}{\constr{\mathbf{0}}}
\newcommand{\comp}[2]{#1 \; \constr{\parallel} \; #2}
\newcommand{\new}{\constr{\boldsymbol{\nu}} \;}
\newcommand{\send}[2]{#1 \; \constr{\langle}#2\constr{\rangle} \;}
\newcommand{\recv}[1]{#1 \; \constr{\mathbb{()}} \;}
\newcommand{\suc}{\constr{\scriptstyle 1+}}
\newcommand{\base}[1]{\constr{B[} \; #1 \; \constr{]}}
\newcommand{\channel}[2]{\constr{C[} \; #1 \; \constr{\propto} \; #2 \; \constr{]}}

@@

% Types
\newcommand{\Set}{\type{SET}}
\newcommand{\reduce}[1]{\; \type{\longrightarrow}_{#1} \;}
\newcommand{\types}[4]{#1 \; \type{\propto} \; #2 \; \type{\vdash} \; #3 \; \type{\boxtimes} \; #4}
\newcommand{\contains}[5]{#1 \; \type{\propto} \; #2 \; \type{\ni} \; #3 \; \type{\propto} \; #4 \; \type{\boxtimes} \; #5}
\newcommand{\Var}{\type{VAR}}
\newcommand{\Process}{\type{PROCESS}}
\newcommand{\Unused}{\type{UNUSED}}
\newcommand{\PreCtx}{\type{PRECTX}}
\newcommand{\Ctx}{\type{CTX}}
\newcommand{\Type}{\type{TYPE}\;}
\newcommand{\Idx}{\type{IDX}\;}
\newcommand{\Idxs}{\type{IDXS}}
\newcommand{\Carrier}{\type{CARRIER}}
\newcommand{\N}{\type{\mathbb{N}}}
\newcommand{\Channel}{\type{CHANNEL}}
\newcommand{\Rec}{\type{REC}}
\newcommand{\Quantifier}{\type{QUANTIFIER}}
\newcommand{\eq}[1]{\; \type{=}_{#1} \;}
\newcommand{\eqeq}{\; \type{\equiv} \;}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule{
      \gamma : \PreCtx_n \\
      \inferrule*{}{
        is : \Idxs_n \\\\
        \Gamma : \Ctx_{is}} \\
      t : \Type \\
      x : \Carrier_i \\
      \Delta : \Ctx_{is}}
    {\contains{\gamma}{\Gamma}{t}{x}{\Delta} : \Set}}

  \inferrule
  {\Gamma : \Ctx_{is} \\ y \; z : \Carrier_i \\ True (\constr{\cdot-compute} \; y \; z)}
  {\constr{zero} : \contains{\gamma , t}{\Gamma , x}{t}{y}{\Gamma , z}}

  \inferrule
  {\Gamma : \Ctx_{is} \\ x : \Carrier_i \\ x' : \Carrier_j \\ \Delta : \Ctx_{is} \\\\
    loc_x : \contains{\gamma}{\Gamma}{t}{x}{\Delta}}
  {\constr{suc} \; loc_x : \contains{\gamma , t}{\Gamma , x'}{t}{x}{\Delta , x'}}
\end{mathpar}
\caption{This is...}
\end{figure}

@@

  {\mprset{fraction={===}}
    \inferrule{
      \gamma : \PreCtx_n \\
      \inferrule*{}{
        is : \Idxs_n \\\\
        \Gamma : \Ctx_{is}} \\
      P : \Process_n \\
      \Delta : \Ctx_{is}}
    {\types{\gamma}{\Gamma}{P}{\Delta} : \Set}}

@@

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{\channel{t}{x}}{\li}{\Xi} \\\\
   cont : \types{\gamma , t}{\Xi , x}{P}{\Theta , \lz}}
  {\constr{recv} \; chan_x \; cont : \types{\gamma}{\Gamma}{\recv{toFin \; chan_x}{P}}{\Theta}}

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{\channel{t}{x}}{\lo}{\Delta} \\\\
   loc_y : \contains{\gamma}{\Delta}{t}{x}{\Xi} \\\\
   cont : \types{\gamma}{\Xi}{P}{\Theta}}
  {\constr{send} \; chan_x \; loc_y \; cont : \types{\gamma}{\Gamma}{\send{toFin \; chan_x}{toFin \; loc_y}P}{\Theta}}

>>>>

% Constructors
\newcommand{\PO}{\constr{\mathbf{0}}}
\newcommand{\comp}[2]{#1 \; \constr{\parallel} \; #2}
\newcommand{\new}{\constr{\boldsymbol{\nu}} \;}
\newcommand{\send}[2]{#1 \; \constr{\langle} \; #2 \;\constr{\rangle} \;}
\newcommand{\recv}[1]{#1 \; \constr{\mathbb{()}} \;}
\newcommand{\suc}{\constr{\scriptstyle 1+}}
\newcommand{\base}[1]{\constr{B[} \; #1 \; \constr{]}}
\newcommand{\channel}[2]{\constr{C[} \; #1 \; \constr{\propto} \; #2 \; \constr{]}}

@@

% Types
\newcommand{\Set}{\type{SET}}
\newcommand{\reduce}[1]{\; \type{\longrightarrow}_{#1} \;}
\newcommand{\types}[4]{#1 \; \type{\propto} \; #2 \; \type{\vdash} \; #3 \; \type{\boxtimes} \; #4}
\newcommand{\contains}[6]{#1 \; \type{\propto} \; #2 \; \type{[} \; #3 \; \type{]\coloneqq} \; #4 \; \type{\propto} \; #5 \; \type{\boxtimes} \; #6}
\newcommand{\Var}{\type{VAR}}
\newcommand{\Process}{\type{PROCESS}}
\newcommand{\Unused}{\type{UNUSED}}
\newcommand{\PreCtx}{\type{PRECTX}}
\newcommand{\Ctx}{\type{CTX}}
\newcommand{\Type}{\type{TYPE}\;}
\newcommand{\Idx}{\type{IDX}\;}
\newcommand{\Idxs}{\type{IDXS}}
\newcommand{\Carrier}{\type{CARRIER}}
\newcommand{\N}{\type{\mathbb{N}}}
\newcommand{\Channel}{\type{CHANNEL}}
\newcommand{\Rec}{\type{REC}}
\newcommand{\Quantifier}{\type{QUANTIFIER}}
\newcommand{\eq}[1]{\; \type{=}_{#1} \;}
\newcommand{\eqeq}{\; \type{\equiv} \;}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule{
      \gamma : \PreCtx_n \\
      \inferrule*{}{
        idxs : \Idxs_n \\\\
        \Gamma : \Ctx_{idxs}} \\
      i : Fin n
      t : \Type \\
      x : \Carrier_i \\
      \Delta : \Ctx_{is}}
    {\contains{\gamma}{\Gamma}{i}{t}{x}{\Delta} : \Set}}

  \inferrule
  {\Gamma : \Ctx_{idxs} \\ y \; z : \Carrier_i \\ True (\constr{\cdot-compute} \; y \; z)}
  {\constr{zero} : \contains{\gamma , t}{\Gamma , x}{zero}{t}{y}{\Gamma , z}}

  \inferrule
  {\Gamma : \Ctx_{idxs} \\ x : \Carrier_i \\ x' : \Carrier_j \\ \Delta : \Ctx_{idxs} \\\\
    loc_x : \contains{\gamma}{\Gamma}{i}{t}{x}{\Delta}}
  {\constr{suc} \; loc_x : \contains{\gamma , t}{\Gamma , x'}{\suc i}{t}{x}{\Delta , x'}}
\end{mathpar}
\caption{This is...}
\end{figure}

@@

  {\mprset{fraction={===}}
    \inferrule{
      \gamma : \PreCtx_n \\
      \inferrule*{}{
        idxs : \Idxs_n \\\\
        \Gamma : \Ctx_{idxs}} \\
      P : \Process_n \\
      \Delta : \Ctx_{idxs}}
    {\types{\gamma}{\Gamma}{P}{\Delta} : \Set}}

@@

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\li}{\Xi} \\\\
   cont : \types{\gamma , t}{\Xi , x}{P}{\Theta , \lz}}
  {\constr{recv} \; chan_x \; cont : \types{\gamma}{\Gamma}{\recv{i}{P}}{\Theta}}

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\lo}{\Delta} \\\\
   loc_y : \contains{\gamma}{\Delta}{j}{t}{x}{\Xi} \\\\
   cont : \types{\gamma}{\Xi}{P}{\Theta}}
  {\constr{send} \; chan_x \; loc_y \; cont : \types{\gamma}{\Gamma}{\send{i}{j}P}{\Theta}}
